\newpage
%\TOCadd{ExecutiveSummary}

\phantomsection

\section*{Acknowledgements}

\paragraph{}
\textbf{Abhishek Bhasin} and \textbf{Isaac Linett} from Q Electrical for their technical assistance and frequent questions.

\paragraph{}
\textbf{Disa} for her constant love and support through not only this project but my entire degree.    

\paragraph{}
My fellow students \textbf{Ash Abdullrabzak} and \textbf{Niroj Gurung} for their valuable discussions throughout our three projects. 

\paragraph{}
\textbf{Associate Profesor Geoffery Walker} for your guidance, support and patience through the completion of this project. 

\paragraph{}
Past Queensland University of Technology engineering student \textbf{Steven Donohue} for his valuable prior thesis on 48V direct current home power systems.  

\newpage


\section*{Executive Summary}

\paragraph{}
This design project aims to solve the issue of incorporating low voltage direct current (DC) power distribution systems to multi-residential and commercial buildings. Low voltage DC power is prevalent in telecommunications systems but has the possibility of being used for a variety of other applications to reduce electricity costs and improve efficiency. Due to the large costs involved in building power systems, the majority of this design project will be completed through software simulations and hand calculations. If these methods cannot be utilised, either physical testing or research will be completed alongside. If successful, a more efficient and cheaper alternative to running simple electronics off of AC mains will be created. This will allow for a portion of building's electricity demands to be self sufficient and not rely on the grid for continual supply.   
 
\newpage
